Turbulence in compact to giant HII regions

### 2022-01-17 strucfunc_paper.tex
Javier changes 2022-01-17

\begin{table}
\begin{center}\caption{Summary of properties of our \hii{} region sample. }
\begin{tabular}{cCCCC}\toprule
\hii{}    &  \text{Distance,}\ D& \text{Diameter,}\ R & \log L(\ha) &  \langle \sigma\los \rangle \\
  Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
\midrule
Orion     & 0.436 \pm 0.02  & 0.6 \pm 0.06    &    37.18       &   6.0      \\
Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   13.6 \pm 0.04     \\
Carina    & 2.35 \pm 0.05   & 15 \pm 1.5      &    38.54    &   22.4 \pm 0.09    \\
30 Dor    & 50.0 \pm 0.2    & 98.9 \pm 9.8    &    39.46    &   31.7     \\
NGC 346   & 62 \pm 1        & 64 \pm 6.4      &    38.77    &   10.1     \\
Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   13.4     \\
Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &   12.3     \\
NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   18.3 \pm 0.06     \\
NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   16.2 \pm 0.08     \\
\bottomrule
\end{tabular}\label{tab:regions-properties}
\end{center}
\end{table}

@@

We can compute the $m_{3D}$ index from the two dimensional \(m\), if we assume that the m$_{3D}$ index lies between the limits of projection smoothing and a sheet-like distribution. 
Following the procedure by \cite{arthur2016turbulence} and assuming the relationship m$_{2D}$ - 1 $<$ m$_{3D}$ $<$ m$_{2D}$ we have 0.36 $<$ m$_{3D}$ $<$ 0.72.

>>>>

\begin{table}
\begin{center}\caption{Summary of properties of our \hii{} region sample. }
\begin{tabular}{cCCCC}\toprule
\hii{}    &  \text{Distance,}\ d& \text{Diameter,}\ D & \log L(\ha) &  \langle \sigma\los \rangle \\
  Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
\midrule
Orion     & 0.436 \pm 0.02  & 0.6 \pm 0.06    &    37.18       &   6.0      \\
Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   13.6 \pm 0.04     \\
Carina    & 2.35 \pm 0.05   & 15 \pm 1.5      &    38.54    &   22.4 \pm 0.09    \\
30 Dor    & 50.0 \pm 0.2    & 98.9 \pm 9.8    &    39.46    &   31.7     \\
NGC 346   & 62 \pm 1        & 64 \pm 6.4      &    38.77    &   10.1     \\
Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   13.4     \\
Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &   12.3     \\
NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   18.3 \pm 0.06     \\
NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   16.2 \pm 0.08     \\
\bottomrule
\end{tabular}\label{tab:regions-properties}
\end{center}
\end{table}

@@

We can compute the $m_{3D}$ index from the two dimensional \(m\), if we assume that the $m_{3D}$ index lies between the limits of projection smoothing and a sheet-like distribution. 
Following the procedure by \cite{arthur2016turbulence} and assuming the relationship $m_{2D}$ - 1 $<$ $m_{3D}$ $<$ $m_{2D}$ we have 0.36 $<$ m$_{3D}$ $<$ 0.72.
